\documentclass[10pt,a4paper]{article}

\usepackage[left=0.8in,right=0.8in,top=0.7in,bottom=0.7in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\setlength{\parindent}{0pt}
\titleformat{\section}{\small\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
{\Large \textbf{DHARSHINI A}}\\
Karaikudi, Tamil Nadu\\
Phone: 9342143286 \;|\;
Email: dharshinia2106@gmail.com\\
LinkedIn: \href{https://www.linkedin.com/in/dharshini0607}{https://www.linkedin.com/in/dharshini0607}\\
GitHub: \href{https://github.com/dharshini-1221}{https://github.com/dharshini-1221}
\end{center}



\section{PROFESSIONAL SUMMARY}
Motivated Bachelor of Science in Information Technology student with strong foundations in programming, data structures, and database management systems. Hands-on experience in Java, Python with DSA, and data analytics tools including Power BI. Actively seeking an entry-level software development or data-related role to apply problem-solving skills, logical thinking, and technical knowledge to real-world applications.

\section{TECHNICAL SKILLS}
\textbf{Programming Languages:} Java, C, C++, Python.\\
\textbf{Web Technologies:} HTML, CSS.\\
\textbf{Data and Analytics Tools:} Power BI, Advanced Excel.\\
\textbf{Databases and Core Concepts:} MySQL, DBMS, Data Structures and Algorithms, Object-Oriented Programming.\\
\textbf{Development Tools and IDEs:} Git, GitHub, Visual Studio Code, Visual Studio .NET,Power BI.\\
\textbf{Soft Skills:} Fast learner, good communication skills, logical thinker.

\section{EDUCATION}
Bachelor of Science in Information Technology\\
Bishop Heber College\\
Year of Passing: 2026\\
Current Academic Performance: 100 Percent

\section{PROJECTS}
\textbf{EduSmartAI}\\
Developed an AI-based educational support system aimed at improving learning efficiency and student engagement. Contributed to logical problem-solving, clean coding practices, and feature optimization to enhance usability and performance.

\textbf{Personal Portfolio Website}\\
Designed and developed a responsive personal portfolio website using HTML and CSS to showcase academic achievements, projects, and technical skills with a user-friendly interface.

\section{INTERNSHIP / TRAINING}
\textbf{Python DSA Intern – T4Tech}\\
Gained hands-on experience in Python programming and data structures by solving algorithmic problems, improving logical reasoning, and strengthening problem-solving skills through practical assignments.

\section{CERTIFICATIONS}
NPTEL Certification in Database Management Systems with a score of 66 percent.\\
IBM Certification in Python Programming with a score of 100 percent.

\section{ACHIEVEMENTS}
Consistent academic performer with strong interest in software development and data analytics. Continuously enhancing skills through certifications, internships, and project-based learning.

\end{document}
